### 2022-11-08 files/Chapter3/dynamicconvergence.tex
klein verbeteringe

Before we can look at the results of \cite{BV13}, some preparation is required. To start, the authors of \cite{BV13} formulate the Galerkin Approximation of Problem GVar.

>>>>

Before the theory of \cite{BV13} can be discussed, some preparation is required. First the Galerkin approximation is for Problem GVar is derived. Then a equivalent system of ordinary differential equations is derived using the Finite Element Method. The problem is then discussed followed by the solution of \cite{BV13}.\\

### 2022-11-08 files/Chapter6/2D_FEM.tex
klein verbeteringe

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
In this chapter, the Finite Element Method (FEM) is applied to the two- and three-dimensional cantilever beams as well as a Reissner-Mindlin cantilever plate. The aim of this chapter is to obtain a numerical formula to calculate the eigenvalues and eigenvectors for these models. This chapter serves as preparation for Chapter 6.\\

The outline of the chapter is as follows.
\begin{itemize}
	\item[] Section \ref{sec:FEM:2D} is the FEM for a two-dimensional cantilever body.
	\item[] Section \ref{sec:FEM:3D} is the FEM for a three-dimensional cantilever body. 
	\item[] Section \ref{sec:FEM:Plate} is the FEM for A Reissner-Mindlin cantilever plate model. 
\end{itemize}

@@

\subsubsection{Cantilever elastic body}
Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries This is referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
\FloatBarrier
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

@@

In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is defined by Problem 2D-1V. For convenience, the relevant results from section \ref{ssec:2D_Model:VariationalForm} are repeated.
\subsubsection{Problem 2D-1V}\label{sssec:2D_Model:Problem2D1VChp5}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{eq:2D_Model:Problem2D1VEqChp5}
\end{align}
for all $\phi \in T(\Omega)$.\\

@@

This form of the bilinear form $b$ is more useful than the general form in \eqref{eq:2D_Model:BilinearChp5} to apply the Finite Element Method.

@@

Define the space
\begin{eqnarray*}
S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right)
\end{eqnarray*}

For each function $u^h \in S^h$, $u^h$ can be expressed as
\begin{eqnarray*}
	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x)
\end{eqnarray*}

@@

\subsubsection{Problem 2D-1G}
Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
\begin{eqnarray*}
	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I \cdot \phi_i)
\end{eqnarray*} for $i = 1,2,...,k$.\\

\textbf{Remarks:}
\begin{itemize}
	\item[] $Q^I$ is scalar vector that is the result of interpolating the function $Q$ over the rectangular grid. i.e. $Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.
\end{itemize}

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
In this chapter, the Finite Element Method (FEM) is applied to the two- and three-dimensional cantilever beams as well as a Reissner-Mindlin cantilever plate. The aim of this chapter is to obtain a numerical formula to calculate the eigenvalues and eigenvectors for these models. This chapter is preparation for Chapter 6.\\

The outline of the chapter is as follows.
\begin{itemize}
	\item[] Section \ref{sec:FEM:2D} FEM for a two-dimensional cantilever body.
	\item[] Section \ref{sec:FEM:3D} FEM for a three-dimensional cantilever body. 
	\item[] Section \ref{sec:FEM:Plate} FEM for A Reissner-Mindlin cantilever plate model. 
\end{itemize}

@@

\subsubsection{Cantilever elastic body}
Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries This is Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
\FloatBarrier
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

@@

In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is defined by Problem 2D-1V. For convenience, some results from section \ref{ssec:2D_Model:VariationalForm} are repeated here.

\subsubsection{Problem 2D-1V}\label{sssec:2D_Model:Problem2D1VChp5}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{eq:2D_Model:Problem2D1VEqChp5}
\end{align}
for all $\phi \in T(\Omega)$.\\

@@

@@

Define the space
\begin{eqnarray*}
S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right).
\end{eqnarray*}

For each function $u^h \in S^h$, $u^h$ can be expressed as
\begin{eqnarray*}
	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x).
\end{eqnarray*}

@@

\subsubsection{Problem 2D-1G}
Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
\begin{eqnarray*}
	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I, \phi_i)
\end{eqnarray*} for $i = 1,2,...,k$.\\

\textbf{Remarks:}
\begin{itemize}
	\item[] $Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$. i.e. $Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.
\end{itemize}
